\documentclass[11pt,a4paper]{altacv}

\geometry{left=1.5cm,right=1.5cm,top=1.cm,bottom=1.2cm,columnsep=1.5cm}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{paracol}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{setspace}

\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{8AC0D9}
\definecolor{PastelRed}{HTML}{00B0DA}
\definecolor{GoldenEarth}{HTML}{B4AD0C}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\familydefault}{\sfdefault}

\name{\Large Guillaume BOILEAU}
\tagline{Scientific Project Manager / Data \& Validation | Coordination, documentation, data quality \& clinical imaging ramp-up}
\personalinfo{
  \email{guillaume.boileaupro@gmail.com}
  \phone{+33 6 59 94 85 84}
  \location{Alpes-Maritimes, France}
  \linkedin{guillaume-boileau-phd-891b81265}
}

\setlength{\parskip}{0.72\baselineskip}

\begin{document}
\makecvheader
\vspace{-0.65cm}

\cvsection{Cover letter}
\vspace{-0.45cm}

{\color{accent}\textbf{Subject:}} \textit{Application -- Project Manager I -- Median Technologies}

{\color{body}

Dear Hiring Team,

I am applying for the \textbf{Project Manager I} position at Median Technologies. The role interests me because it combines scientific project coordination, data quality, documentation, study follow-up, communication with technical and business stakeholders, and rigorous compliance with procedures. These are areas where my background in R\&D, data, validation and international collaboration can bring value.

My profile is not that of a clinical project manager by initial training. It is the profile of a scientific and technical project-oriented engineer, used to working with complex data, structured documentation, validation workflows, discrepancy analysis and cross-functional contributors. I am now looking to apply this experience in a healthcare and clinical-imaging environment, with a focused ramp-up on clinical trials, GCP, site management and Median's internal procedures.

At \textbf{CNES}, I worked on the ground segment of the LISA ESA/NASA space mission. This environment required rigorous coordination, traceability, data management, validation and documentation. I developed \textbf{CATpyLISA}, a Python platform used to structure data workflows, compare models, validate results and prepare technical review material. This experience gave me a strong habit of tracking deliverables, documenting assumptions and deviations, preparing review-ready outputs, and coordinating with several scientific, software and institutional contributors.

More recently, at \textbf{VEV Platform Services France}, I worked on an operational software platform connected to field infrastructure. I contributed to data-flow analysis, incident investigation, data inconsistency analysis, documentation and follow-up of corrective actions. This experience is directly relevant to the reconciliation and discrepancy-management mindset required in your role: identify inconsistencies, document them clearly, support resolution and maintain reliable information for the team.

At \textbf{Universiteit Antwerpen}, I worked as a Data Scientist on complex sensor datasets, statistical modelling and performance validation. I produced analyses, figures of merit, technical reports and recommendations for international stakeholders. This strengthened my ability to manage data quality, validate results, communicate clearly in English and work with multidisciplinary teams.

For Median Technologies, I can bring scientific rigour, strong written and oral English, excellent documentation habits, data-management skills, and the ability to communicate between technical and business functions. I am comfortable organising information, writing clear minutes and technical summaries, tracking actions, supporting project status reporting and ensuring that procedures are followed.

I am also very motivated by the opportunity to enter the clinical imaging and pharma project environment. I understand that the role involves study support, PSR editing, meeting organisation, minutes, study binder completion, training-record tracking, reconciliation reports, site initiation support, escalation logs and procedure compliance. These topics are new in their clinical context, but they are close to the way I already work: structured follow-up, rigorous documentation, discrepancy analysis, traceability and communication.

I would be glad to discuss how my experience in scientific coordination, data quality, validation, documentation and international communication can contribute to Median Technologies' project teams.

Yours sincerely,

\textbf{Guillaume Boileau}

}

\end{document}
