\documentclass[11pt,a4paper]{altacv}

\geometry{left=1.5cm,right=1.5cm,top=1.cm,bottom=1.2cm,columnsep=1.5cm}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{paracol}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{setspace}

\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{8AC0D9}
\definecolor{PastelRed}{HTML}{00B0DA}
\definecolor{GoldenEarth}{HTML}{B4AD0C}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\familydefault}{\sfdefault}

\name{\Large Guillaume BOILEAU}
\tagline{Scientific Project Manager / Data \& Validation | Project coordination, documentation, reconciliation \& clinical imaging ramp-up}
\personalinfo{
  \email{guillaume.boileaupro@gmail.com}
  \phone{+33 6 59 94 85 84}
  \location{Alpes-Maritimes, France}
  \linkedin{guillaume-boileau-phd-891b81265}
}

\setlength{\parskip}{0.72\baselineskip}

\begin{document}
\makecvheader
\vspace{-0.65cm}

\cvsection{Cover letter}
\vspace{-0.45cm}

{\color{accent}\textbf{Subject:}} \textit{Application -- Project Manager I -- Median Technologies}

{\color{body}

Dear Hiring Team,

I am applying for the \textbf{Project Manager I} position at Median Technologies. Your offer particularly interests me because it combines project coordination, scientific data management, documentation, reconciliation, communication with technical and business teams, and strict adherence to project procedures. These are areas where my experience in R\&D, software, data validation and international scientific collaboration is directly relevant.

I hold a PhD in Physics and have built my career in environments where complex projects require structure, rigour and clear communication. I have worked with heterogeneous datasets, technical contributors, validation workflows, documented procedures, review material and discrepancy analysis. This background gives me a strong foundation to manage and support customer projects, track actions, prepare reliable documentation, and contribute to the smooth execution of study-related activities.

At \textbf{CNES}, I worked on the ground segment of the LISA ESA/NASA space mission. This role required the coordination of scientific and software contributors, the tracking of technical deliverables, the preparation of review material, and the validation of complex data products. I developed \textbf{CATpyLISA}, a Python platform used to structure datasets, compare models, validate outputs and document deviations. This experience is highly relevant to project management activities such as maintaining clear project status, following procedures, ensuring traceability, supporting reviews, and communicating effectively with different stakeholders.

A central part of my work has always been documentation and follow-up. I am used to writing technical summaries, documenting assumptions, preparing review material, tracking open points, clarifying responsibilities and making sure that information remains understandable and usable by the whole team. This is directly aligned with the responsibilities described in your offer: organising meetings, writing minutes, completing study documentation, tracking training records, supporting study management and reporting project status to senior project managers.

My recent experience at \textbf{VEV Platform Services France} strengthened my operational mindset. I worked on a software platform connected to field infrastructure, where I analysed data flows, investigated incidents, documented anomalies and followed corrective actions with technical teams. This experience is particularly relevant to the reconciliation part of the role. I am comfortable identifying inconsistencies in data, analysing their possible causes, documenting findings and supporting resolution in a structured way.

At \textbf{Universiteit Antwerpen}, I worked as a Data Scientist on complex sensor datasets, statistical modelling and performance validation. I developed workflows to verify data consistency, compare configurations, assess uncertainty and produce technical reports for international stakeholders. This experience supports several skills required by Median Technologies: statistics, data management, communication in English, scientific rigour and the ability to work across technical and functional areas.

Although I have not yet worked directly in clinical trials or medical imaging project management, I bring a strong scientific background and the right working habits for this environment: precision, traceability, documentation, data quality, procedure compliance and structured communication. I am motivated to build on this foundation and ramp up quickly on GCP, clinical research processes, site management, study binder requirements, PSR editing, training-record tracking and Median Technologies' internal procedures.

I can bring value to your squad by supporting project execution with reliability and clarity: organising information, preparing meetings, writing minutes, following actions, supporting project coordinators and site managers, helping with escalation logs, documenting discrepancies, and maintaining a clear view of project progress, risks and priorities. I am also comfortable working in English with international teams and adapting my communication to both technical and business audiences.

Median Technologies operates at the intersection of medical imaging, software, data and clinical research. This is precisely the type of environment where my combined experience in science, data, validation, software and coordination can be useful. I would be pleased to contribute to your pharma customer projects with rigour, organisation and a strong sense of responsibility.

I would be glad to discuss how my experience in project coordination, data quality, validation, documentation and international communication can support Median Technologies' project teams.

Yours sincerely,

\textbf{Guillaume Boileau}

}

\end{document}
